---
title: "Project 1 answers"
author: "Practical Lecture 7"
date: "January 22, 2020"
output:
  pdf_document: default
  html_document: default
editor_options:
  chunk_output_type: console
---

## R Training Project

The data was collected on the use of mobile money services and the experiences of mobile money customers in three districts of Rwanda. The dataset has been provided and you have been asked to write a short summary outlining key findings from the project. You should perform all the statistical analysis required and write up the key findings. You should remember that the target audiences do not have a statistical background. You can access the tasks of this project [here](https://github.com/vmandela99/Project1)

The research manager wants you to address the following points in the key findings:

1.	Clean the data before undertaking any analysis

```{r import, include=FALSE}
library(tidyverse)
library(scales)
library
theme_set(theme_light())

#load the data
proj_data <- read_csv("https://raw.githubusercontent.com/vmandela99/Project1/master/mobilemoney_data.csv")

#clean the data
##remove incomplete entries
clean_data <- proj_data %>% na_if(" ") %>% drop_na()
```

```{r echo=FALSE}
clean_data %>% head(5)%>% knitr::kable()
```


2.	Select the variables, "age", "gender", "education level" and "number of household members" in R and write them in a new and separate file. Save the data set as "demographics.csv"

```{r include=FALSE}
#view the data names
names(clean_data)
```

```{r echo=TRUE}
#extract the variables of interest
demographics <- clean_data %>% select(7:10)

#This code exports to demographics.csv
#write_csv(demographics,"demographics.csv")
```

3.	Conduct exploratory analysis of the data and write a few bullet points on any descriptive statistics (summary statistics, tables and graphs) you find interesting and why you find them interesting.

```{r include=FALSE}
skimr::skim(clean_data)
```

```{r echo=TRUE}
#count
demographics %>% count(gender,name = "frequency") %>% mutate(percentage = round(frequency/sum(frequency),4)*100) %>% knitr::kable(caption = "Table showing frequency of Gender", col.names = c("Gender","Frequency","Perc"))
```

In the mobile money data survey the complete information was from 38 female and 81 males. 

```{r echo=TRUE}
demographics %>% count(factor(hh_members)) %>% rename(members=`factor(hh_members)`) %>%  mutate(percentage = round(n/sum(n),4)*100, members =fct_reorder(members,n))%>% ggplot(aes(x = members ,y = percentage))+ geom_col(fill = "navy blue") + coord_flip() + labs(x = "# of household members", y = "percentage frequency", title = "In most of the houses, how many people lived there?", subtitle = "most households had 4 and 3 members") + theme_bw()+ scale_y_continuous(
  breaks = c(10, 20),
  label = c("ten %", "twenty %")
)
```

4.	During the survey, participants listed all the different types of financial accounts that they have registered. The resulting data has a format where there is one observation per account type. Format the data so that there is now one observation participant. Save data as mobile_new.csv 

```{r}

#spread the acoount type column using the account number as values
clean_data %>% pivot_wider(names_from =  account_type,values_from =  account_num) -> mobile_new

#to write a new data set
#write.csv(mobile_new, "mobile_new.csv")
```

The procedure we used was to spread the types of accounts column and we end up with one observation for each person, regardless the number of accounts they have.

5.	Describe how the mobile money market is divided between the three companies. Include at least one chart or table to illustrate your findings.

```{r}
clean_data %>% ggplot(aes(x= mm_account_telco_main, y = 1,fill = account_type)) + geom_col(position = "stack") + labs(y = "frequency of bank accounts", x = "Type of Company", title = "how is the mobile money market is divided between the three companies?", subtitle = "dd")
```

```{r}
clean_data %>% group_by(mm_account_telco_main)%>% count(mm_account_telco_main,account_type) %>% mutate(perc = n/sum(n)*100) %>% arrange(desc(perc)) %>% knitr::kable()

```


6.	Develop a cross tabulation (in percentages) with gender as the rows and columns with urban, mm_trust and prefer_cash

```{r include=FALSE}
cross_data <- clean_data %>% select(gender,urban,mm_trust,prefer_cash)

new_croo <- cross_data %>% mutate(urban1 = as.numeric( fct_anon(factor(urban))),
                      mm_tust1 = as.numeric(fct_anon(factor(mm_trust))),
                      prefer_cash1 = as.numeric(fct_anon(factor(prefer_cash))))  

new_croo %>% group_by(gender) %>% summarise(urban_perc = sum(urban1))
```

7.	Plot the graph of gender and mm_account in the same bar graph and clearly label your axis

```{r}
proj_data %>% ggplot(aes(x= gender, y = 1,fill = mm_account)) + geom_col(position = "stack") + labs(x = "Gender of the respondents", y = "Frequency", title = "How many people have accounts by gender?", subtitle = "78.6% of males had accounts as compared to 61%. 38.1% of women had no accounts as compared to 21.4%")
```














